---
title: "Introduction to Data Visualization with `ggplot2`"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---


```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(mosaic)
library(dplyr)

ALL_AS_EXERCISE = TRUE  # switch between interactive online activities (true means interactive)
EVAL_HO_BLOCKS  = FALSE # code that only executes in student handouts
FIG_HEIGHT = 2

# Read data from greenhouse game 
GreenHouse<- readr::read_csv("https://www.stat2games.sites.grinnell.edu/data/greenhouse/getdata.php") 
GreenHouse <- select(GreenHouse, Crop, Money, Water, Nitrates, Yield, Profit)

colleges <- read.csv("https://remiller1450.github.io/data/Colleges2019.csv")
```



<!-- START_SECTION -->
## Getting Started

This online tutorial is designed to introduce you to data visualization and how to create high quality graphics using the `ggplot2` package.

### Packages and Datasets

You will need the following packages to complete this tutorial:

```{r load_packages, eval = EVAL_HO_BLOCKS}
# install.packages("ggplot2")
library(ggplot2)
```

You will also need the following datasets:

```{r load_datasets, eval = EVAL_HO_BLOCKS}
# Read data from greenhouse game
GreenHouse<- readr::read_csv("https://www.stat2games.sites.grinnell.edu/data/greenhouse/getdata.php") 
GreenHouse <- select(GreenHouse, Crop, Money, Water, Nitrates, Yield, Profit)

# Read other data (you can read them later in the lab)
# colleges <- read.csv("https://remiller1450.github.io/data/Colleges2019.csv")
# approval <- read.csv("https://bit.ly/398YR6M")
```

**Note:** In this tutorial we will use "cleaned data"; you will learn how to manipulate data prior to graphing in subsequent tutorials.
<!-- END_SECTION -->


<!-- START_SECTION -->
## Introduction

This tutorial will focus on creating graphs to effectively communicate key patterns within a dataset. While many software packages allow the user to make basic plots, it can be challenging to create plots that are customized to address a specific idea. There are numerous ways to create graphs, however this tutorial will focus on the `R` package `ggplot2`, created by Hadley Wickham.

The key function used in `ggplot2` is `ggplot()` (the *grammar of graphics plot*). This function is different from other graphics functions because it uses a particular grammar inspired by Leland Wilkinson's landmark book, *The Grammar of Graphics*, that focused on thinking about, reasoning with and communicating with graphics. It enables layering of independent components to create custom graphics.

**Data**: In this tutorial, we will use the [data](https://stat2games.sites.grinnell.edu/data/greenhouse/greenhouse.php) from [Greenhouse Game](https://stat2games.sites.grinnell.edu/), which provides yielding information in a virtual greenhouse. 

To start, we've paired down the dataset to focus on just a few variables:

 * `Crop`: The type of crops (Beans, Corn, or Tomato) planted in a plot
 * `Money`: The amount of money that the player currently have (start with 5000; calculated each season)
 * `Water`: The amount of water (in inches) that you assign to a plot
 * `Nitrate`: The amount of nitrates that exists within a plot
 * `Yield`: The amount of crops produced on a plot
 * `Profit`: The amount of money you earned on a plot
 
Run the following code to get a peak of the Greenhouse data:

```{r display_data, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE}
# The code below uses the head() function to view the first four lines of the Greenhouse data.
head(GreenHouse, 4)
```
<!-- END_SECTION -->


<!-- START_SECTION -->
## Overview of the `ggplot2` Framework

### Terminology
The `ggplot2` framework is unique because all graphics are grammatically defined using the following terminology:

 * **Geometric Elements** (or "**geom**"): this determines the type of geometric shape used to display the data (i.e. lines, bars, points, areas, etc.)
 * **Aesthetics** (or "**aes**"): this determines how variables in the data are mapped to visual properties of **geom**s (i.e. $x$ position, $y$ position, color, shape, fill, size, etc.)
 * **Scales**: guidelines for how aesthetic mappings should be displayed (i.e. logarithmic $x$-axis, red to blue color palate, etc.)
 * **Guides** (or "legends"): references to help a human reader interpret the aesthetics
 * **Facets**: rules specifying how to break up and separately display subsets of data

### The Structure of the `ggplot` Function
All `ggplot` functions must have at least three components:

 * **data**: specifies what to plot; this could be via the inclusion of a data frame, or explicitly specified as needed,
 * **geom**: specifies what type of plot, and
 * **aes**: specifies how to plot the data.

Thus the structure of a graphic made with `ggplot()` could have the following form:

<h4 style = "text-align: center;" markdown = "1"> ggplot(data = , mapping = aes(x = , y = )) + geom_***() </h4>

In the following histogram we use `Water` as the $x$ variable:

```{r example_hist_1, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, message = FALSE}
ggplot(data = GreenHouse, mapping = aes(x = Water)) + geom_histogram()
```

In the above code, the terms `data =` and `mapping =` are not required (nor is `x =` since it is a one variable plot), but are used for clarification. For example, the following code will produce the same result:

```{r example_hist_2, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, message = FALSE}
ggplot(GreenHouse, aes(Water)) + geom_histogram()
```

**Note:** The terms `data =` and `mapping =` are not required if and only if both are supplied in the appropriate order; the first and second arguments are always presumed to be `data` and `mapping`, respectively (unless otherwise specified).

### How `ggplot2` Creates Graphics

The `ggplot2` package builds graphics in a structured manner using layers. Layers are sequentially added to a graph, with each serving a particular purpose, such as:
1. Displaying raw data
2. Displaying a statistical summary
3. Adding metadata (i.e. annotations, context, references, etc.)

Consider the following examples:

#### Example 1.1a - nothing (just a base layer)

```{r example_base_layer_1_1, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot()
```

#### Example 1.1b - again a base layer, but now with specified data and axes

```{r example_base_layer_1_2, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(data = GreenHouse, mapping = aes(x = Water, y = Yield))
```

#### Example 1.2 - add a layer displaying raw data, here as a scatter plot with "points"

```{r example_add_layer_1, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(data = GreenHouse, mapping = aes(x = Water, y = Yield)) +
  geom_point()
```

Notice the addition of the "+" sign after the first line, this indicates that an additional layer will follow.

#### Example 1.3 - add another layer (a smooth fit)

```{r example_add_layer_2, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(data = GreenHouse, mapping = aes(x = Water, y = Yield)) +
  geom_point() +
  geom_smooth()
```

#### Example 1.4 - add another layer (reference text)

```{r example_add_layer_3, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(data = GreenHouse, mapping = aes(x = Water, y = Yield)) +
  geom_point() +
  geom_smooth() +
  annotate("text", x = 75, y = 20, label = "Yield Data based on Different Water Levels")
```

**Note:** A high-quality graphic doesn't require any particular number of layers. In fact, more layers can sometimes detract from the clarity of a data visualization.

### More on the Base Layer

The data and mapping arguments provided in the base layer are carried forward to all subsequent layers (which is often desirable). However, we can avoid this behavior in a variety of ways:

#### Example 2.1 - distinguishing data points by the type of crop with a color aesthetic

```{r example_more_base_layer_1, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(data = GreenHouse, mapping = aes(x = Water, y = Yield, color = Crop)) +
  geom_point()
```

#### Example 2.2 - a local override of the color aesthetic

```{r example_more_base_layer_2, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(data = GreenHouse, mapping = aes(x = Water, y = Yield, color = Crop)) +
  geom_point(color = "red")
```

#### Example 2.3 - specifying aesthetics locally within layers

```{r example_more_base_layer_3, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(data = GreenHouse) +
  geom_point(mapping = aes(x = Water, y = Yield, color = Crop)) +
  geom_smooth(mapping = aes(x = Water, y = Yield, color = Crop))
```

Local aesthetic specification is most useful when you want to add layers that involve the same parameters ("$x$" and "$y$") but for different things. Common examples are drawing a line through several different group means of an ordinal categorical variable, or displaying both polygons and points on a map.

#### Example 2.4 - specifying data locally within layers

```{r example_more_base_layer_4, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(mapping = aes(x = Water, y = Yield)) +
  geom_point(data = subset(GreenHouse, Crop == "Tomato"), color = "red") +
  geom_point(data = subset(GreenHouse, Crop == "Beans"),   color = "blue")
```

Local data specification is most useful when you want to include data from different sources (that again use the same parameters).

<!-- START_QUESTION -->
#### Question #1:

Identify and briefly describe each term mentioned above in the graphic created by the code below:

```{r question_code_parts, eval = TRUE, warning = FALSE, fig.height = 3}
## Data processing
colleges <- read.csv("https://remiller1450.github.io/data/Colleges2019.csv")

## Creating the graph
ggplot(data = colleges, mapping = aes(x = Adm_Rate, color = Private)) +
  geom_density() +
  scale_x_continuous(trans = "reverse") +
  facet_wrap(~Region)
```
<!-- END_QUESTION -->

<!-- START_QUESTION -->
#### Question #2:

Create a histogram of the variable "Enrollment" displayed on the log2-scale and faceted by the variable "Private". Use the ggplot2 cheatsheet to help you identify the necessary functions and arguments.
<!-- END_QUESTION -->
<!-- END_SECTION -->


<!-- START_SECTION -->
## Themes
Themes are pre-built style templates used to better tailor a graphic to the mode of publication.

The example below applies a black and white theme to Example 2.1 from above:

```{r example_theme_1, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(data = GreenHouse, mapping = aes(x = Water, y = Yield, color = Crop)) +
  geom_point() +
  theme_bw()
```

Other pre-built themes:

 * `theme_bw()`
 * `theme_linedraw()`, `theme_light()`, and `theme_dark()`
 * `theme_minimal()`
 * `theme_classic()`
 * `theme_void()`

You can judge the differences in these themes below:

```{r, echo = FALSE, fig.height = 4}
library(patchwork)
x <- c(1, 2, 3)
y <- c(1, 2, 3)
plot1 <- ggplot(mapping = aes(x = x, y = y)) +
           geom_point() +
           labs(title = "theme_grey()") +
           theme_grey() +
           theme(plot.title = element_text(hjust = 0.5))
plot2 <- ggplot(mapping = aes(x = x, y = y)) +
           geom_point() +
           labs(title = "theme_bw()") +
           theme_bw() +
           theme(plot.title = element_text(hjust = 0.5))
plot3 <- ggplot(mapping = aes(x = x, y = y)) +
           geom_point() +
           labs(title = "theme_linedraw()") +
           theme_linedraw() +
           theme(plot.title = element_text(hjust = 0.5))
plot4 <- ggplot(mapping = aes(x = x, y = y)) +
           geom_point() +
           labs(title = "theme_light()") +
           theme_light() +
           theme(plot.title = element_text(hjust = 0.5))
plot5 <- ggplot(mapping = aes(x = x, y = y)) +
           geom_point() +
           labs(title = "theme_dark()") +
           theme_dark() +
           theme(plot.title = element_text(hjust = 0.5))
plot6 <- ggplot(mapping = aes(x = x, y = y)) +
           geom_point() +
           labs(title = "theme_minimal()") +
           theme_minimal() +
           theme(plot.title = element_text(hjust = 0.5))
plot7 <- ggplot(mapping = aes(x = x, y = y)) +
           geom_point() +
           labs(title = "theme_classic()") +
           theme_classic() +
           theme(plot.title = element_text(hjust = 0.5))
plot8 <- ggplot(mapping = aes(x = x, y = y)) +
           geom_point() +
           labs(title = "theme_void()") +
           theme_void() +
           theme(plot.title = element_text(hjust = 0.5))
(plot1 | plot2 | plot3 | plot4) / (plot5 | plot6 | plot7 | plot8)
```

Any theme can be further customized using `theme()`. Most commonly this function is used to remove a graph's legend:

```{r example_theme_3, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(data = GreenHouse, mapping = aes(x = Water, y = Yield, color = Crop)) +
  geom_point() +
  theme_bw() +
  theme(legend.position = "none")
```

<!-- START_QUESTION -->
#### Question #3:

The code below creates a line graph that depicts (via a smoothed moving average) the approval of former presidents Jimmy Carter, Ronald Reagan, and Barrack Obama. Modify second portion of this code to try out a few different non-default themes. Then, briefly discuss (1-2 sentences) which themes you feel are most effective and least effective for this type of graph. Include the graph with your preferred theme in your lab write-up.

```{r example_theme_4, eval = TRUE, fig.height = 3}
## Data processing
approval <- read.csv("https://bit.ly/398YR6M")
approval$Week = as.numeric(difftime(as.Date(approval$End.Date, "%m/%d/%y"), as.Date(approval$Inaug.Date, "%m/%d/%y"), units = "weeks"))
approval2 = subset(approval, President %in% c("Reagan", "Carter", "Obama"))

## Creating the graph
ggplot(data = approval2, mapping = aes(x = Week, y = Approving, color = President)) +
 geom_smooth(method = "loess", span = 0.6, se = FALSE)
```
<!-- END_QUESTION -->
<!-- END_SECTION -->


<!-- START_SECTION -->
## Labels and Annotations
Labels and annotations are important aspects of well-constructed data visualizations. They are used to provide context, or draw the viewer's attention towards particular aspects of the graphic.

Labels corresponding to *aesthetics* (such as `x`, `y`, `color`, etc.) are controlled using the `labs()` function:

```{r labels_1, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(data = GreenHouse, mapping = aes(x = Water, y = Yield, color = Crop)) +
  geom_point() +
  theme_bw() +
  labs(x = "Water Level", y = "Yield", color = "Crop")
```

Annotations are added the graphic as a layer using the `annotate()` function:

```{r labels_2, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(data = GreenHouse, mapping = aes(x = Water, y = Yield, color = Crop)) +
  geom_point() +
  theme_bw() +
  labs(x = "Water Level", y = "Yield", color = "Crop") +
  annotate(geom = "rect", xmin = 20, xmax = 40, ymin = 10, ymax = 25, color = "red", alpha = 0.2)
```

The example above annotates a scatter plot by drawing a red rectangle with 20% transparency (controlled by `alpha = `) around the cluster of the most corns

#### Question #4:

Use the `subset()` function to create a data frame containing only colleges located in the state of Iowa. Using these data, create a box plot of admissions rates, rename the $x$-axis label to "Admissions Rate", and add a text annotation above the outlier saying "Grinnell".
<!-- END_SECTION -->

