---
title: "Visualizating the GreenHouse Data"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---


```{r setup, include=FALSE}
library(learnr)
library(readr)
library(ggplot2)
library(mosaic)
library(dplyr)
library(easydox)

ALL_AS_EXERCISE = TRUE  # switch between interactive online activities (true means interactive)
EVAL_HO_BLOCKS  = FALSE # code that only executes in student handouts
FIG_HEIGHT = 2

# Read data from greenhouse game 
GreenHouse<- read_csv("https://www.stat2games.sites.grinnell.edu/data/greenhouse/getdata.php") 
GreenHouse <- select(GreenHouse, GroupID, PlayerID, Plot,Season, Level, Crop, Water, Nitrates, Yield, Profit)
sample1 <- read.csv("Sample1_data.csv")

#sample1 <- read_csv("Sample1_data.csv")
sample1 <- select(sample1, GroupID, PlayerID, Plot, Season, Level, Crop, Water, Nitrates, Yield, Profit)

```



<!-- START_SECTION -->
## Getting Started

This online tutorial is designed to demonstrate how to use R to create graphs with the Greenhouse data. In this page, you will be able to type code into any of the boxes below. If it doesn't work, simply try a "hint" or click the "start Over" button. If you have never written R code before, you might choose to work through an [Introduction to R](https://shiny.grinnell.edu/tutorials/1_R_Intro/#section-getting-started) before attempting this activity.


**Data**: In this tutorial, we will use the data from the [Greenhouse Game](https://stat2games.sites.grinnell.edu/), which provides information from a virtual greenhouse. We also have a specific small set of Greenhouse data called **sample1**. You can download the sample1 data from the app on the last page of this tutorial.

We will use just a few variables that are available within the full Greenhouse data set.

 * `GroupID`: Any alpha‐numeric term used for each class or team
 * `PlayerID`: Any alpha‐numeric term used for each player
 * `Level`: Level of the Greenhouse game
 * `Plot`: The area of ground for planting seeds, plots are numbered between 1 and 40
 * `Crop`: The type of crops (Beans, Corn, or Tomato) grown in each plot
 * `Water`: The amount of water (in inches) that is given to each plot
 * `Nitrate`: The amount of nitrates in the soil of each plot
 * `Yield`: The amount of crops produced. It is measured by the number of bushels produced for each plot. 
 * `Profit`: The amount of money earned on a plot
 

Before making a graph, we will use a few commands that allow us to view the data sets. Select the **Run Code** button on the right to run the code in each of the sections below.

```{r display_data, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE}
# The code below reads the Greenhouse data and then views the first four lines of the Greenhouse data.
GreenHouse<- read_csv("https://www.stat2games.sites.grinnell.edu/data/greenhouse/getdata.php") 
head(GreenHouse, 4)

# The code below uses the head() function to view the first four lines of the sample1 data, which has alredy been read into this tutorial.
head(sample1, 4)
```

```{r display_summary_data, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE}
# The code below uses the str() command to see each column of the Greenhouse sample1 data.
str(sample1)
```

```{r display_summary_stats, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE}
# The code below used the favstats() command to see summary statistics of 'Yield' variable in the Greenhouse sample1 data.
favstats(sample1$Yield)
```


**Questions:**  

1) Try modifying the above code to determine the number of rows in the Greenhouse data set. 

```{r 1d,exercise=TRUE,exercise.lines=3}

```


```{r 1d-hint-1}
# Notice that the str() command shows the dimensions of a data set.
```

```{r 1d-hint-2}
str(GreenHouse)
```


2) What code could you use to find the average Profit from the sample1 data?

```{r 1e,exercise=TRUE,exercise.lines=3}

```



```{r 1e-hint-1}
# Try the favstats() command, but select Profit instead of Yield
```

```{r 1e-hint-2}
favstats(sample1$Profit)
```



<!-- END_SECTION -->



<!-- START_SECTION -->
## Our First Graph

If you worked through the GreenHouse activity, you have already used an app to create a scatterplot of the sample1 data.
```{r display_plot, echo = FALSE}
ggplot(aes(x = Water, y = Yield), data = sample1) +
  labs(title="Scatterplot of Amount of Water versus Yield") +
  geom_point() 
```

Whenever we write code it is important to be able to clearly understand the following two questions. 

1. What do you want the computer to do?
2. What must the computer know in order to do that?

To make the above plot, the answers to our questions are

1. **What we want the computer to do:**

      *	Make a scatter plot
      * A	better answer: a plot consisting of points

2. **What the computer needs to know:** The data used for the plot
      
      *	The variable to be plotted along the y-axis.
      *	The variable to be plotted along the x-axis.
      *	The data set that contains the variables.

While many software packages allow the user to make basic plots, it can be challenging to create plots that are customized to address a specific idea. While there are numerous ways to create graphs, this tutorial will focus on the R package ggplot2, created by Hadley Wickham. The key function we will use is `ggplot()`. 

### Plot Template

All of our graphs will have the same basic template to identify the needed information, as shown below:

<h4 style="text-align: center;">
  ggplot( aes(
  <span style="border: 2px solid gray; padding: 2px;">x</span>
  ,
  <span style="border: 2px solid gray; padding: 2px;">y</span>
  ), data =
  <span style="border: 2px solid gray; padding: 2px;">mydata</span>
  ) + 
  <span style="border: 2px solid gray; padding: 2px;">goal</span>
</h4>

<br>
where the pieces in the boxes can be replaces with specific variables to achieve different purposes:

<!-- make the table -->
<div style="display: flex; justify-content: center; align-items: center; margin-bottom: 20px;">
  <table border="1" style="width: 60%; border-collapse: collapse; text-align: center;">
    <tr>
      <th>Box</th>
      <th>Specific Information</th>
      <th>Purpose</th>
    </tr>
    <tr>
      <td>Y</td>
      <td>Yield</td>
      <td>y-axis variable</td>
    </tr>
    <tr>
      <td>X</td>
      <td>Water</td>
      <td>x-axis variable</td>
    </tr>
    <tr>
      <td>mydata</td>
      <td>sample1</td>
      <td>name of data set</td>
    </tr>
    <tr>
      <td>goal</td>
      <td>geom_point()</td>
      <td>plot some points</td>
    </tr>
  </table>
</div>


Now, we can put each piece in its place in the template and then run the code to create the plot.

### Make your first graph

```{r create_plot1, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE}
# The code below uses ggplot() and geom_point() to create a scatterplot of Water versus Yield

ggplot(aes(x = Water, y = Yield), data = sample1) +
  geom_point() 
```


**Questions:**  

3) Create a new scatterplot of Water versus Profits using the sample1  data.

```{r 2d,exercise=TRUE,exercise.lines=3}

```


```{r 2d-hint-1}
# Replace y = Yield with y = Profit
```

```{r 2d-hint-2}

ggplot(aes(x = Water, y = Profit), data = sample1) +
  geom_point() 
```

<!-- END_SECTION -->

<!-- START_SECTION -->

## Layering Graphs with ggplot2

While many software packages allow the user to make basic plots, it can be challenging to create plots that are customized to address a specific idea. One advantage of the `ggplot()` function is that it enables independent components to be layered to create custom graphics.

For example, we can add a regression line to our scatterplot:

### Adding a regression line to your scatterplot

```{r add_regline, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# The code below adds a linear regression line to the scatterplot or water versus yield

ggplot( aes(x = Water, y = Yield), data = sample1) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```


**Questions:**  

4) Create 4 new graphs using the following code and explain what each of the following does.

4a.

```{r exercise2a, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# Remove `,se=FALSE`
ggplot( aes(x = Water, y = Yield), data = sample1) +
  geom_point() +
  geom_smooth(method = "lm")
```
 

4b. 

```{r exercise2b, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# Remove `method = "lm”, se = FALSE`
ggplot( aes(x = Water, y = Yield), data = sample1) +
  geom_point() +
  geom_smooth()
```

4c.

```{r exercise2c, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# Add `, formula = y ~ poly(x, 2)` after `method = "lm` to create a quadratic line
ggplot( aes(x = Water, y = Yield), data = sample1) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), se=FALSE)
```

4d.

```{r exercise2d, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# Add `, formula = y ~ poly(x, 2)` and remove `,se=FALSE`
ggplot( aes(x = Water, y = Yield), data = sample1) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2))
```


**Note:** A high-quality graphic doesn't require any particular number of layers. In fact, more layers can sometimes detract from the clarity of a data visualization.
<!-- END_SECTION -->


<!-- START_SECTION -->
## Coloring, Faceting, and Other Aesthetics

After building layers for generating the basics of the plot, we can use different aesthetics to enhance the visualizations. For example, we can use color to distinguish data points, facet data to create subplots, as well as adjust the transparency, size, and shape of points.

### Coloring and Overriding Aesthetics

The following example shows how coloring helps distinguish between different categories within our data.

#### Example 1.1 - distinguishing data points by the type of crop with a color aesthetic in the base layer
```{r example_more_base_layer_1, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(data = sample1, mapping = aes(x = Water, y = Yield, color = Crop)) +
  geom_point()
```

After adding the color aesthetics on the base layer, we can override aesthetics locally within other layers, so that some layers can have different aesthetics than others.

#### Example 1.2 - a local override of the color aesthetic

```{r example_more_base_layer_2, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(data = sample1, mapping = aes(x = Water, y = Yield, color = Crop)) +
  geom_point(color = "red")
```

Instead of apply aesthetic to the base layer, we can also apply locally within layers. This allows for different aesthetics to be applied to different layers of the same plot.

#### Example 1.3 - specifying aesthetics locally within layers

```{r example_more_base_layer_3, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(data = sample1) +
  geom_point(mapping = aes(x = Water, y = Yield, color = Crop)) +
  geom_smooth(mapping = aes(x = Water, y = Yield, color = Crop))
```

Local aesthetic specification is most useful when you want to add layers that involve the same parameters ("$x$" and "$y$") but for different things. Common examples are drawing a line through several different group means of an ordinal categorical variable, or displaying both polygons and points on a map.

#### Example 1.4 - specifying data locally within layers

```{r example_more_base_layer_4, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(mapping = aes(x = Water, y = Yield)) +
  geom_point(data = subset(sample1, Crop == "Tomato"), color = "red") +
  geom_point(data = subset(sample1, Crop == "Beans"),   color = "blue")
```

Local data specification is most useful when you want to include data from different sources (that again use the same parameters).


### Faceting

Faceting allows us to split our plot into multiple subplots based on the levels of some variable in the data set. In the `ggplot2` package, the function `facet_wrap()` is commonly used for faceting the plot.

#### Example 2.1 - Faceting by Crop
```{r example_facet1, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# The code below uses `facet_warp()` to split the plot based on Crop variable.
ggplot(data = sample1, mapping = aes(x = Water, y = Yield)) +
  geom_point() +
  facet_wrap(~Crop)
```

#### Example 2.2 - Faceting by Level
```{r example_facet2, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# The code below uses `facet_warp()` to split the plot based on Level variable.
ggplot(data = sample1, mapping = aes(x = Water, y = Yield)) +
  geom_point() +
  facet_wrap(~Level)
```

### Other Aesthetics
Now, let's look at some other ways to adjust the aesthetics of our plot.

#### Example 3.1 - adjusting transparency (`alpha`) of data points
```{r example_aes1, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# The code below adjusts the transparency of all data points
ggplot(data = sample1, mapping = aes(x = Water, y = Yield)) +
  geom_point(alpha = 0.5)
```

#### Example 3.2 - adjusting `size` of data points
```{r example_aes2, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# The code below adjusts the size of all data points
ggplot(data = sample1, mapping = aes(x = Water, y = Yield)) +
  geom_point(size = 0.5)
```

#### Example 3.3 - adjusting `shape` of data points
```{r example_aes3, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# The code below adjusts the shape of all data points to square
ggplot(data = sample1, mapping = aes(x = Water, y = Yield)) +
  geom_point(shape = 0)
```
Here are some other commonly used values for `shape`:

  * shape = 1, circle
  * shape = 2, triangle point up
  * shape = 3, plus
  * shape = 4, cross
  * shape = 5, diamond
  * shape = 6, triangle point down
  * shape = 7, square cross
  * shape = 8, star
  * shape = 9, diamond plus
  * shape = 10, circle plus

#### Example 3.4 - distinguishing data points by the type of crop with different `shape` of data points
```{r example_aes4, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# The code below applies a distinct shape to the data points of each crops
ggplot(data = sample1, mapping = aes(x = Water, y = Yield, shape = Crop)) +
  geom_point()
```

#### Example 3.5 - Adjusting `linetype`
```{r example_aes5, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# The code below adjusts the linetype for the regression line 
ggplot(aes(x = Water, y = Yield), data = sample1) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed")
```
Other `linetype` values include "dotted", "dotdash", "longdash", "twodash", "solid",  and "twodash". You can try to change the value and observe the changes.


### Exercise 3: Use the given scatterplot to create following visualizations
```{r exercise3, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(aes(x = Water, y = Profit), data = sample1) +
  geom_point()
```

#### a. Color by Nitrates and adjust transparency to 0.8 for all data points:

```{r exercise3a, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# Write your code here

```

#### b. Facet by Level and adjust point size to 2:

```{r exercise3b, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# Write your code here

```

#### c. Add a linear regression line and change the line type to "dotted"

```{r exercise3c, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# Write your code here

```
<!-- END_SECTION -->


<!-- START_SECTION -->
## Themes
Themes are pre-built style templates used to better tailor a graphic to the mode of publication.

### Applying Pre-built Theme
#### Example 4.1: applying bw theme
```{r example_theme_1, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# The code below applies the bw theme to the plot
ggplot(data = sample1, mapping = aes(x = Water, y = Yield, color = Crop)) +
  geom_point() +
  theme_bw()
```

Other pre-built themes:

 * `theme_bw()`
 * `theme_linedraw()`, `theme_light()`, and `theme_dark()`
 * `theme_minimal()`
 * `theme_classic()`
 * `theme_void()`

You can judge the differences in these themes below:

```{r, echo = FALSE, fig.height = 4}
library(patchwork)
x <- c(1, 2, 3)
y <- c(1, 2, 3)
plot1 <- ggplot(mapping = aes(x = x, y = y)) +
           geom_point() +
           labs(title = "theme_grey()") +
           theme_grey() +
           theme(plot.title = element_text(hjust = 0.5))
plot2 <- ggplot(mapping = aes(x = x, y = y)) +
           geom_point() +
           labs(title = "theme_bw()") +
           theme_bw() +
           theme(plot.title = element_text(hjust = 0.5))
plot3 <- ggplot(mapping = aes(x = x, y = y)) +
           geom_point() +
           labs(title = "theme_linedraw()") +
           theme_linedraw() +
           theme(plot.title = element_text(hjust = 0.5))
plot4 <- ggplot(mapping = aes(x = x, y = y)) +
           geom_point() +
           labs(title = "theme_light()") +
           theme_light() +
           theme(plot.title = element_text(hjust = 0.5))
plot5 <- ggplot(mapping = aes(x = x, y = y)) +
           geom_point() +
           labs(title = "theme_dark()") +
           theme_dark() +
           theme(plot.title = element_text(hjust = 0.5))
plot6 <- ggplot(mapping = aes(x = x, y = y)) +
           geom_point() +
           labs(title = "theme_minimal()") +
           theme_minimal() +
           theme(plot.title = element_text(hjust = 0.5))
plot7 <- ggplot(mapping = aes(x = x, y = y)) +
           geom_point() +
           labs(title = "theme_classic()") +
           theme_classic() +
           theme(plot.title = element_text(hjust = 0.5))
plot8 <- ggplot(mapping = aes(x = x, y = y)) +
           geom_point() +
           labs(title = "theme_void()") +
           theme_void() +
           theme(plot.title = element_text(hjust = 0.5))
(plot1 | plot2 | plot3 | plot4) / (plot5 | plot6 | plot7 | plot8)
```


### Customizing Themes

After applying the pre-built theme, we can also add customized features using `theme()` function. Most commonly this function is used to remove a graph's legend:

#### Example 4.2: removing graph's legend from pre-built theme
```{r example_theme_3, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# The code below adds a bw theme and uses `theme()` to remove the graph's legend
ggplot(data = sample1, mapping = aes(x = Water, y = Yield, color = Crop)) +
  geom_point() +
  theme_bw() +
  theme(legend.position = "none")
```

#### Example 4.3: adding customized features to the theme
```{r example_theme_4, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# The code below customizes font size, color, and type for title and axes
ggplot(data = sample1, mapping = aes(x = Water, y = Yield, color = Crop)) +
  geom_point() +
  labs(title = "Yield vs Water", x = "Water", y = "Yield") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 20, face = "bold", color = "gray"),
    axis.title.x = element_text(size = 14, face = "italic", color = "darkblue"),
    axis.title.y = element_text(size = 14, face = "italic", color = "darkblue"),
    axis.text = element_text(size = 12)
  )

```

### Exercise 4: Apply and customize themes
#### a. Use GreenHouse data to create a scatterplot of water versus profit and apply the classic theme to the plot using `theme_classic()`

```{r exercise4a, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# Write your code here

```

#### b. Add 3 customized features to the classic theme

```{r exercise4b, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# Write your code here

```

<!-- END_SECTION -->


<!-- START_SECTION -->
## Labels and Annotations
Labels and annotations are important aspects of well-constructed data visualizations. They are used to provide context, or draw the viewer's attention towards particular aspects of the graphic.

Labels corresponding to *aesthetics* (such as `x`, `y`, `color`, etc.) are controlled using the `labs()` function:

```{r labels_1, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(data = sample1, mapping = aes(x = Water, y = Yield, color = Crop)) +
  geom_point() +
  theme_bw() +
  labs(x = "Water Level", y = "Yield", color = "Crop")
```

Annotations are added the graphic as a layer using the `annotate()` function:

```{r labels_2, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
ggplot(data = sample1, mapping = aes(x = Water, y = Yield, color = Crop)) +
  geom_point() +
  theme_bw() +
  labs(x = "Water Level", y = "Yield", color = "Crop") +
  annotate(geom = "rect", xmin = 20, xmax = 40, ymin = 10, ymax = 25, color = "red", alpha = 0.2)
```

The example above annotates a scatter plot by drawing a red rectangle with 20% transparency (controlled by `alpha = `) around the cluster of the most corns

<!-- END_SECTION -->


<!-- START_SECTION -->
## Residual Plot


In the previous part, we have learnt about adding a regression line to our graph. However, notice that there are various points that do not fall on the line. In fact, most of them don't. How do we visualize the distance of each point to the fitted line. Here, we will draw residual plots that can show us the distribution of the residuals of the points in our data. 

First, let's start with a simple linear regression model to predict Yield from Water and draw the residual plots of it. To fit a linear regression model in R, we will use the function `lm()`. Then, we can use `resid` to extract model residuals from the model returned by `lm()`.

### Generate residuals from linear regression model and create a histogram of residuals
```{r residual_plost1, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE}
myModel <- lm(Yield ~ Water, data = sample1)
res <- resid(myModel)

hist(res, main = "Histogram of Residuals", xlab = "Residuals")
```

### Create Normal Q-Q Plot of Residuals
```{r residual_plost2, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE }
myModel <- lm(Yield ~ Water, data = sample1)
res <- resid(myModel)

qqnorm(res, main = "Normal Q-Q Plot of Residuals")
qqline(res)
```

### Create plot of Water vs Residuals
```{r residual_plost3, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE }
myModel <- lm(Yield ~ Water, data = sample1)
res <- resid(myModel)

plot(sample1$Water, res, 
     main = "Water vs. Residuals",
     xlab = "Water", 
     ylab = "Residuals")
abline(h = 0)
```

We can also combine all 3 plots into a page by using `par(mfrow = c(2,2))`

### Combine the above residual plots
```{r residual_plost4, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE }
myModel <- lm(Yield ~ Water, data = sample1)
res <- resid(myModel)
par(mfrow = c(2,2))
# Create histogram of residuals
hist(res, main = "Histogram of Residuals", xlab = "Residuals")
# Create normall qq plot
qqnorm(res, main = "Normal Q-Q Plot of Residuals")
qqline(res)
# Create plot of Water vs Residuals
plot(sample1$Water, res, 
     main = "Water vs. Residuals",
     xlab = "Water", 
     ylab = "Residuals")
abline(h = 0)
```


### Exercise 5: Add residual plots 
#### a. Fit a linear regression model to predict profit from water and extract the model residuals.
```{r exercise5a, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# Write your code here

```

#### b. Create a plot of water versus residuals 

```{r exercise5b, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# Write your code here

```

<!-- END_SECTION -->


<!-- START_SECTION -->
## Let’s test your skills!
Here are two apps that helps you do the data wrangling and create visualizations using Greenhouse data. Feel free to play around with them to generate different plots you like and observe the code behind the plots!

(need the link for the shiny apps to be added here)
```{r, echo=FALSE}
knitr::include_app(" https://shiny.grinnell.edu/GHTutorial/", height = "500px")
```

### Exercise 6: Try to create the following plots on you own and check your answers using the above apps.
#### a. 
```{r echo =FALSE}
# Remove `method = "lm”, se = FALSE`
ggplot(aes(x = Water, y = Yield, shape = Crop, color = Crop), data = sample1) +
  geom_point() +
  labs(title = "Yield vs Water by Level", x = "Water", y = "Yield") +
  facet_wrap(~Level) +
  theme_light() +
  theme(
    axis.title.x = element_text(size = 14, face = "italic", color = "darkblue"),
    axis.title.y = element_text(size = 14, face = "italic", color = "darkblue"),
    axis.text = element_text(size = 12)
  )
```

```{r exercise6a, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# Write your code here

```

#### b. 
```{r echo =FALSE}
# Remove `method = "lm”, se = FALSE`
ggplot(aes(x = Water, y = Yield, color = Level), data = sample1) +
  labs(title = "Yield vs Water by Crop", x = "Water", y = "Yield") +
  geom_point() +
  facet_wrap(~Crop)
```

```{r exercise6b, exercise = ALL_AS_EXERCISE, eval = !ALL_AS_EXERCISE, fig.height = FIG_HEIGHT}
# Write your code here

```
<!-- END_SECTION -->
